False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-08-24 ms.tex
edits

\newcommand{\ntotal}{8826}
\newcommand{\nfail}{787}
\newcommand{\ncalc}{8039}
\newcommand{\nval}{1500}
\newcommand{\nvalnew}{1000}
\newcommand{\nfp}{500}
\newcommand{\nfpnew}{200}
\newcommand{\nbadphot}{47} %EmptyPhotometry or MissingKOI
\newcommand{\nbadphotFP}{34}
\newcommand{\nbadphotCAND}{13}
\newcommand{\nbadrowemcmc}{216}
\newcommand{\nbadstellar}{98} %MissingStellar
\newcommand{\nbadsec}{162} %NoWeakSecondary
\newcommand{\nattempted}{8141}
\newcommand{\ntryfail}{112}
\newcommand{\nbadtrapfit}{32}
\newcommand{\nbadroche}{52}
\newcommand{\nbadother}{28}
\newcommand{\nbadotherFP}{22}
\newcommand{\nbadotherCAND}{5}
\newcommand{\nbadotherCONF}{1}

@@

Of the \ntotal\ KOIs in the cumulative
table at the NExScI Exoplanet Archive, \vespa\ successfully
calculated the FPP for \ncalc.  Many of the \nfail\ failures are a
result of a KOI no longer being ``of interest,'' despite still
being listed in the cumulative table.  \sect{failures} contains
detailed explanations of the different failure modes.

>>>>

\newcommand{\ntotal}{8826}
\newcommand{\nfail}{787}
\newcommand{\ncalc}{8039}

\newcommand{\nvalnew}{1000}
\newcommand{\nfp}{500}
\newcommand{\nfpnew}{200}
\newcommand{\nbadphot}{47} %EmptyPhotometry or MissingKOI
\newcommand{\nbadphotFP}{34}
\newcommand{\nbadphotCAND}{13}
\newcommand{\nbadrowemcmc}{216}
\newcommand{\nbadstellar}{98} %MissingStellar
\newcommand{\nbadsec}{162} %NoWeakSecondary
\newcommand{\nattempted}{8141}
\newcommand{\ntryfail}{112}
\newcommand{\nbadtrapfit}{32}
\newcommand{\nbadroche}{52}
\newcommand{\nbadother}{28}
\newcommand{\nbadotherFP}{22}
\newcommand{\nbadotherCAND}{5}
\newcommand{\nbadotherCONF}{1}

\newcommand{\nreliable}{2854}
\newcommand{\nval}{2136}
\newcommand{\nreliableFP}{298}

@@

Of the \ntotal\ KOIs in the cumulative table at the NExScI Exoplanet
Archive, \vespa\ successfully calculated the FPP for \ncalc.  These
results are listed in \tab{fpp};  \sect{failures} contains detailed
explanations of the different failure modes.

The first thing to note about these results is that they should not
all be taken at face value.  For example, many KOIs have already been
identified as false positives, and designated

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
\end{center}
\caption{False positive probabilities of all KOIs for which we
  consider the \vespa\ calculations to be reliable.  This includes
  KOIs that are not dispositioned as FALSE POSITIVE on the NExScI
  archive, are considered to be reliably located on the target star ($
  {\rm Pr} > 0.99$) according to pixel-level analysis
  \citep{Bryson:2015}, and for which $\mathcal L_{\rm tot} > 10^{-3}$,
  indicating that the hypotheses tested by \vespa\ are not all poor
  explanations of the data.  Of these \nreliable\ KOIs, \nval\ have
  FPPs less than 1\%.  Noteably, \nreliableFP\ are likely false
  positives (FPP $> 0.5$), consistent with the \citet{Morton:2011} and
  \citet{Fressin:2013} \emph{a priori} estimates of the overall
  \kepler\ candidate false positive rate.

\figlabel{fppall}}
\end{figure*}
